Causal Inference in the 2020 US Federal Election: While COVID-19 Lowered Trump's Support, Loss of Confidence Among Wealthier Voters Seems More Decisive

### 2023-12-11 outputs/paper/paper.qmd
Try MatchIt

@@

>>>>

```{r}
data <- read.csv(here("outputs/data/merged_data.csv"))

library(MatchIt)
m.out <- matchit(treatment ~ prop_higher_education + pctile + 
                       no_insurance + private_insurance + males +
                       white_pct + black_pct,
                 data = data,
                 distance = "logit",
                 method = "nearest",
                 replace = FALSE,
                 ratio = 1)
summary(m.out, standardize = TRUE)
```

@@

```{r}

```
